---
title: "Multi Source Plots Playground"
output: html_notebook
---

# Multi Source Plots Playground
Show the overlap between multi-sources, comparing predicted & true labels

## Load data and libraries
```{r}
# Install missing libraries
#install.packages("ggupset")
# install.packages("ggpattern")

# Load libraries
library(tidyverse)
library(ggupset)
library(ggpattern)
```

Load the data
Set indicies, set multi-source flags, join the two dataframes by columns
```{r}
# Set the paths
data_path = "../00_Data/export"

model_name = "Bio_ClinicalBERT"

bert_predictions_path = sprintf("%s/%s_predictions.csv", data_path, model_name)
bert_true_path = sprintf("%s/%s_true_labels.csv", data_path, model_name)

# Load the files
bert_true_tbl <- read_csv(bert_true_path, show_col_types = FALSE) %>%
  mutate(across(where(is.numeric), as.logical)) %>%
  select(-uncertainty)  

bert_predictions_tbl <- read_csv(bert_predictions_path, show_col_types = FALSE) %>%
    mutate(across(where(is.numeric), as.logical)) %>%
  select(-uncertainty)  

# Get indication list
indication_list <- colnames(bert_predictions_tbl)
```

## Preprocess the data
```{r}
# Prefix the prediction columns
bert_predictions <- bert_predictions_tbl %>%
  rename_with(~ paste0("pred_", .x))

# Check for multi-source indications
bert_true <- bert_true_tbl %>%
  rowwise() %>%
  mutate(is_multisource=sum(c_across(where(is.logical))) > 1) %>%
  ungroup()

bert_predictions <- bert_predictions %>%
  rowwise() %>%
  mutate(pred_is_multisource=sum(c_across(where(is.logical))) > 1) %>%
  ungroup()

# Join the two DFs
multi_indications <- bert_true %>%
  # Move raw indications to the index | later this could be patient IDs
  remove_rownames() %>%
  column_to_rownames(var = "IndicationRaw") %>%
  # Join with the predicted labels
  bind_cols(bert_predictions)
```

## Data Processing
Count the number of overlaps in the groups

```{r}
# Get indication list
vis_data <- multi_indications %>%
  # Filter for multisource & only true label data
  filter(is_multisource) %>%
  select(-starts_with("pred_"), -is_multisource) %>%
  # Reshape the data
  as_tibble(rownames = "IndicationRaw") %>%
  gather(Indication, Value, -IndicationRaw) %>%
  filter(Value) %>%
  group_by(IndicationRaw) %>%
  summarize(Indication = list(Indication))

vis_data
```

```{r}
# Get indication list
vis_data2 <- multi_indications %>%
  # Filter for multisource & only true label data
  filter(pred_is_multisource) %>%
  select(starts_with("pred_"), -pred_is_multisource) %>%
  rename_with(~ str_remove( .x, "pred_")) %>%
  # Reshape the data
  as_tibble(rownames = "IndicationRaw") %>%
  gather(Indication, Value, -IndicationRaw) %>%
  filter(Value) %>%
  group_by(IndicationRaw) %>%
  summarize(Indication = list(Indication)) %>%
  # Add marker
  mutate(predicted=TRUE)

vis_data2
```

```{r}
vis_data_full <- vis_data %>%
  mutate(predicted=FALSE) %>%
  bind_rows(vis_data2)
vis_data_full
```

## Plot as upset plot
Plot the given dataset
```{r}
vis_data_full %>%
    ggplot(aes(x=Indication)) +
    geom_bar(aes(fill=predicted), position = position_dodge(preserve = "single")) +
scale_x_upset(n_intersections = 20)
```

## Full custom plot
Create dummy data
```{r}
ind_a <- "Respiratory"
ind_b <- "Urinary"

source_a <- "True Label"
source_b <- "Predicted Label"

expl_data <- tibble(
  Indication = list(c(ind_a, ind_b), c(ind_a, ind_b), c(ind_a, ind_b)),
  Dummy = c("One", "One", "One"),
  Source = c(source_a, source_b, source_b),
  Size = c(3, 2, -2),
  IsOverlapping = c(TRUE, TRUE, FALSE)
)
expl_data
```
Upset version
```{r}
ggplot(expl_data, aes(x=Indication)) +
  geom_col(aes(y=Size, fill=Source,  alpha=IsOverlapping, group=Source), position="dodge") +
  scale_alpha_discrete(range = c(0.4, 1.0)) +
  scale_x_upset(n_intersections = 20)
```

With shaded area
```{r}
ggplot(expl_data, aes(x=Indication)) +
  geom_col_pattern(aes(y=Size, fill=Source,  pattern_density=IsOverlapping, group=Source), 
                   pattern_fill = "white",
                   pattern_colour = "white",
                   position="dodge") +
  scale_pattern_density_manual(values = c("TRUE" = 0.0, "FALSE"=0.1)) +
  scale_x_upset(n_intersections = 20)
```