---
title: "Extract indication colum in MIMIC-ED"
output: html_notebook
---

Use the true free-text column `chiefcomplaint` from the `triage.csv` file, which was taken at the start of a visit.
It respresents the main complaint (and should reflect the reason medication was given).

Processing idea: Filter ED visits for ones where ABX were given.

Tasks:
1. Filter for ABX prescriptions in `pyxis.csv`
2. Join the ABX prescriptions with the triage data

pysis |><| edstays (on: [subject_id, stay_id])


## Load libraries and data
Load libraries
```{r}
library(readr)
library(dplyr)
library(stringr)
```

Load data
```{r}
base_data_path <- "~/DPhil/Projects/EHR-Indication-Processing/99_Sandbox/MIMIC/physionet.org/files/mimic-iv-ed/2.2/ed/"

# Medication
phyxis <- read_csv(paste0(base_data_path, "pyxis.csv"), col_types = cols(
  subject_id = col_double(),
  stay_id = col_double(),
  charttime = col_datetime(format = ""),
  med_rn = col_double(),
  name = col_character(),
  gsn_rn = col_double(),
  gsn = col_character()
))

# Triage
triage <- read_csv(paste0(base_data_path, "triage.csv"), col_types = cols(
  subject_id = col_double(),
  stay_id = col_double(),
  temperature = col_double(),
  heartrate = col_double(),
  resprate = col_double(),
  o2sat = col_double(),
  sbp = col_double(),
  dbp = col_double(),
  pain = col_character(),
  acuity = col_double(),
  chiefcomplaint = col_character()
))

```

## Filter and Match
Filter phyxis for ABX based on the GSN column

```{r}
phyxis %>%
  filter(str_detect(etcdescription, "(?i)antibiotic"))

```



