---
title: "Population Statistics"
output: html_notebook
---

Figures and tables for the results section, based on the raw, unprocessed and unlabelled data.

## Load libraries and data
```{r}
library(tidyverse)
library(lubridate) 
```

Specify data paths and global settings
```{r}
# --- Define the base paths
base_data_path <- "../../00_Data/"

# Final data path
test_set_path <- paste(base_data_path, "data_sets", sep = "/")

# Look up table path
lut_path <- paste0(base_data_path, "LUTs/")

# Max decimal places to round to
round_decimals = 0
```

Load the data
```{r}
# --- EHR Data
# Load the whole antibiotic prescription dataset
antibiotic_prescription_oxford <-   read_csv(paste0(test_set_path, "/Oxford/Full_Oxford_Data_Set.csv"), col_types = cols(
  ClusterID = col_double(),
  PrescriptionID = col_character(),
  Indication = col_character(),
  PrescriptionDate = col_datetime(format = ""),
  PrescriptionStatus = col_character(),
  PrescriptionType = col_character(),
  AdmissionDate = col_date(format = ""),
  Drug = col_character(),
  Formulation = col_character(),
  Dose = col_double(),
  DoseUnit = col_character(),
  Frequency = col_character(),
  Route = col_character(),
  ScheduledStartDateTime = col_datetime(format = ""),
  ScheduledStopDateTime = col_datetime(format = ""),
  DurationEnteredByPrescriber = col_character(),
  ReviewDateTime = col_datetime(format = ""),
  FirstAdministrationDateTime = col_datetime(format = ""),
  LastAdministrationDateTime = col_datetime(format = ""),
  NumberOfDosesAdministered = col_double(),
  SpecialInstructions = col_character(),
  AntibioticsSource = col_character(),
  LinkedBirthMonth = col_datetime(format = ""),
  Age = col_double(),
  WardStartDate = col_datetime(format = ""),
  WardEndDate = col_datetime(format = ""),
  Facility = col_character(),
  Location = col_character()
))

antibiotic_prescription_banbury <-   read_csv(paste0(test_set_path, "/Banbury/Full_Banbury_Data_Set.csv"), col_types = cols(
  ClusterID = col_double(),
  PrescriptionID = col_character(),
  Indication = col_character(),
  PrescriptionDate = col_datetime(format = ""),
  PrescriptionStatus = col_character(),
  PrescriptionType = col_character(),
  AdmissionDate = col_date(format = ""),
  Drug = col_character(),
  Formulation = col_character(),
  Dose = col_double(),
  DoseUnit = col_character(),
  Frequency = col_character(),
  Route = col_character(),
  ScheduledStartDateTime = col_datetime(format = ""),
  ScheduledStopDateTime = col_datetime(format = ""),
  DurationEnteredByPrescriber = col_character(),
  ReviewDateTime = col_datetime(format = ""),
  FirstAdministrationDateTime = col_datetime(format = ""),
  LastAdministrationDateTime = col_datetime(format = ""),
  NumberOfDosesAdministered = col_double(),
  SpecialInstructions = col_character(),
  AntibioticsSource = col_character(),
  LinkedBirthMonth = col_datetime(format = ""),
  Age = col_double(),
  WardStartDate = col_datetime(format = ""),
  WardEndDate = col_datetime(format = ""),
  Facility = col_character(),
  Location = col_character()
))

# Episodes Dataset
episodes_full <-  read_csv("~/shared/iord_extract_20220325/inpt_episode.csv", col_types = cols(
    ClusterID = col_double(),
    LinkedBirthMonth = col_datetime(),
    LinkedSex  = col_factor()
))

# Exact Prescribing Consultant Information
episode_speciality <- episodes_full %>%
  distinct(ClusterID, EpisodeID, ConsultantMainSpecialtyCode)

# Extract Demographics information (contains birth year & month, Sex)
patient_demographics <- episodes_full %>%
  distinct(ClusterID, LinkedSex)

# --- LUTs
nhs_speciality_lut <- read_csv(paste0(lut_path, "NHS_Main_Speciality_Code.csv"), show_col_types = FALSE)
```

## [Check] Duplicates
No duplicates in the prescriptions data (ClusterID and PrescriptionID are primary keys)
```{r}
print("Oxford")
# Print all prescriptions with multiple entries
antibiotic_prescription_oxford %>%
  group_by(ClusterID, PrescriptionID) %>%
  filter(n() > 1)

print("Banbury")
# Print all prescriptions with multiple entries
antibiotic_prescription_banbury %>%
  group_by(ClusterID, PrescriptionID) %>%
  filter(n() > 1)
```
-> Pass, all unique

No duplicates within the dempographics information
```{r}
# Print all ClusterIDs with more than one entry
patient_demographics %>%
  group_by(ClusterID) %>%
  filter(n() > 1)
```
-> Pass, no duplicated entries

## [Result] Data Set Size
Number of unique patients and prescriptions
```{r}
data_set_size <- function(data, location){
  data %>%
    summarise(
      Location=location,
      `Unique Patients`=length(unique(ClusterID)),
      `Unqiue Prescriptions`=length(unique(PrescriptionID))
    )
}


# Oxford
data_set_size(antibiotic_prescription_oxford, "Oxford")

# Banbury
data_set_size(antibiotic_prescription_banbury, "Banbury")
```

## [Result] Unique indications
```{r}
unique_indications <- function(data, location){
  unique_count <- data %>%
    distinct(Indication) %>%
    nrow()
  print(paste0("Unique indications in ", location, ": ", unique_count))
}

# Oxford
unique_indications(antibiotic_prescription_oxford, "Oxford")

# Banbury
unique_indications(antibiotic_prescription_banbury, "Banbury")
```


## [Result] Data Inclusion Dates
Get the date ranges for our data
```{r}

date_ranges <- function(data, location){
  data %>%
    summarise(
      Location=location,
      `First Date`=min(PrescriptionDate),
      `Last Date`=max(PrescriptionDate)
    )
}

# Oxford
date_ranges(antibiotic_prescription_oxford, "Oxford")

# Banbury
date_ranges(antibiotic_prescription_banbury, "Banbury")
```

## [Result] Most commonly prescribed ABX
```{r}
most_prescribed_abx <- function(data, location){
  data %>%
    count(Drug, name = "Count", sort = TRUE) %>%
    mutate(Percentage=(Count/sum(Count) * 100) %>% round(round_decimals) %>% paste0("%")) %>%
    rename(!!paste0("Drug ", location) := Drug)
}

# Oxford
most_prescribed_abx(antibiotic_prescription_oxford, "Oxford") %>%
  head(10) %>%
  as.data.frame() %>%
  knitr::kable()
# Banbury
most_prescribed_abx(antibiotic_prescription_banbury, "Banbury") %>%
  head(10) %>%
  as.data.frame() %>%
  knitr::kable()
```

## [Result] Consultant main speciality
```{r}
consultant_main_speciality <- function(data, location){
  data %>%
    # Join the prescriptions with specialties
    inner_join(episode_speciality, by = join_by(ClusterID, EpisodeID), relationship = "many-to-one") %>%
    # Make the ConsultantMainSpecialityCode field human readable
    left_join(nhs_speciality_lut, by = join_by(ConsultantMainSpecialtyCode == MainSpecialtyCode)) %>%
    count(MainSpecialtyDescription, name = "Count", sort = TRUE) %>%
    mutate(Percentage=(Count/sum(Count) * 100) %>% round(round_decimals) %>% paste0("%")) %>%
    rename(!!paste0("MainSpecialtyDescription ", location) := MainSpecialtyDescription)
}
# Oxford
consultant_main_speciality(antibiotic_prescription_oxford, "Oxford") %>%
  head(10) %>%
  as.data.frame() %>%
  knitr::kable()

# Banbury
consultant_main_speciality(antibiotic_prescription_banbury, "Banbury") %>%
  head(10) %>%
  as.data.frame() %>%
  knitr::kable()
```

## [Result] Demographic
Age & Sex

Calculate the age at first admission
```{r}
patient_age_demographics <- function(data, location){
  # Get the demographics information for our subset
  patient_demographics_filtered <- data %>%
    # Join the prescriptions with demographics
    inner_join(patient_demographics, by = join_by(ClusterID), relationship = "many-to-one") %>%
    # Take only the first admission
    arrange(ClusterID, AdmissionDate) %>%
    distinct(ClusterID, .keep_all = TRUE) %>%
    select(ClusterID, Age, LinkedSex)
  
  patient_demographics_filtered %>%
    summarise(
      Location=location,
      `Age Median`=median(Age) %>% round(round_decimals),
      `Age Q1`=quantile(Age, prob=c(.25)) %>% round(round_decimals),
      `Age Q3`=quantile(Age, prob=c(.75)) %>% round(round_decimals),
      `Age IQR`=IQR(Age) %>% round(round_decimals),
      `Female %`=sum((LinkedSex=="F")/n()*100) %>% round(round_decimals),
      `Female Count`=sum((LinkedSex=="F")) %>% round(round_decimals)
      )
    
}

# Oxford
patient_age_demographics(antibiotic_prescription_oxford, "Oxford")

# Banbury
patient_age_demographics(antibiotic_prescription_banbury, "Banbury")
```


## [Result] Prescription Indications
- Unique indications 
- Top k most frequent ones
- Top k least frequent ones
- Misspellings

Number of unique indications [duplicate]
```{r}
antibiotic_prescription_oxford %>%
  summarise(
    `Total Indications`=n(),
    `Unique Indications`=length(unique(Indication))
  )
```

Top k most common and least common indications
```{r}
top_k_common <- 100 # e.g. top 10 or top 100

# Count the indications
antibiotic_prescription_unique <- antibiotic_prescription_oxford %>%
  count(Indication, sort = TRUE) %>%
  mutate(Percentage=(n/sum(n) * 100) %>% round(round_decimals))

antibiotic_prescription_unique %>%
  head(top_k_common) %>%
  rename(`Indication Common`=Indication) %>%
  print()

antibiotic_prescription_unique %>%
  tail(top_k_common) %>%
  rename(`Indication Uncommon`=Indication) %>%
  print()

antibiotic_prescription_unique %>%
  filter(Indication %in% c("transplant pyelonephritis", "ludwig's angina", "deep neck infection")) %>%
  print()
```
Misspellings
```{r}
antibiotic_prescription_unique %>%
  filter(5 <= n, n <= 100) %>%  # Filter out the most common ones, for data governance reason keep a min of 5
  sample_n(10) %>%  # Randomly sample 10, as they are currently ordered alphabetically
  mutate(
    n=case_when(
      n < 10 ~ "<10",
      TRUE ~ as.character(n)
      ),
      Percentage=case_when(
        Percentage == 0 ~ "<1%",
        TRUE ~ paste0(Percentage, "%")
      )
    ) %>%
  as.data.frame() %>%
  knitr::kable()
```
-> Just find random ones. Spesis instead of sepsis is common.


