---
title: "Multisource Plot"
output: html_notebook
---

# Multi Source Plots 
Show the overlap between multi-sources, comparing predicted & true labels

## Load data and libraries
```{r}
# Install missing libraries
# install.packages("ggupset")
# remotes::install_github("coolbutuseless/ggpattern")


# Load libraries
library(tidyverse)
library(ggupset)
library(ggpattern)
```
```{r}
clean_category_names <- function(input_df){
  old_names <- colnames(input_df)
  
  # Replace dashes with spaces and capitalize
  new_names <- old_names %>%
    gsub("_", " ", .) %>%  # replace underscores with spaces
    tools::toTitleCase()   # capitalize first letter of each word
  
  # Handle specific cases
  new_names <- new_names %>%
    gsub("Ent", "ENT", .)  # replace 'Ent' with 'ENT'
  
  # Assign the new names back to the dataframe
  colnames(input_df) <- new_names
  
  return(input_df)
}
```

Load the data
Set indices, set multi-source flags, join the two data frames by columns
```{r}
# --- Set the paths
data_path = "../00_Data/"
plot_path <- paste0(data_path, "publication_ready/plots/")

model_name = "Bio_ClinicalBERT"
test_location = "banbury"

bert_predictions_path = sprintf("%s/export/%s/%s_%s_predictions.csv", data_path, model_name, model_name, test_location)
bert_true_path = sprintf("%s/publication_ready/testing_%s_2023-08-23.csv", data_path, test_location)

# --- Load the files
bert_predictions_tbl <- read_csv(bert_predictions_path, show_col_types = FALSE)
bert_true_tbl <- read_csv(bert_true_path, show_col_types = FALSE)

# --- Clean/reformat the data
# Convert integers to logical, remove uncertainty column, add indication raw column
bert_true <- bert_true_tbl %>%
  mutate(across(where(is.numeric), as.logical)) %>%
  select(-uncertainty, -PrescriptionID) %>%
  clean_category_names

bert_predictions <-  bert_predictions_tbl %>%
  mutate(across(where(is.numeric), as.logical)) %>%
  select(-uncertainty) %>%
  mutate(Indication = bert_true$Indication) %>%
  clean_category_names

# --- Get indication list
indication_list <- colnames(bert_predictions_tbl)
```

## Preprocess and reshape the data
1. Get a list of indication (or ID) -> Multilevel source list
2. Combine rows & flag (add indicator for truth, icd, indication)
   Compare to truth and flag incorrect ones
3. Count occurrences per group and combine the data frames

1. Aggregate to multi-sources
```{r}
multi_true <- bert_true %>%
  pivot_longer(!Indication) %>%
  filter(value) %>%
  group_by(Indication) %>%
  # Renmove duplicates
  distinct(name, .keep_all = TRUE) %>%
  # Take only the detected source
  filter(n()>1) %>%
  summarise(Source=list(sort(name)))
```

```{r}
multi_predictions <- bert_predictions %>%
  pivot_longer(!Indication) %>%
  filter(value) %>%
  group_by(Indication) %>%
  # Take only the detected source
  filter(n()>1) %>%
  summarise(Source=list(sort(name)))
```

2. Combine and add indicator for matching
```{r}
multi_true_matching <- multi_true %>%
  mutate(Matching=TRUE)
```

```{r}
multi_predictions_matching <- multi_predictions %>%
  left_join(multi_true, 
            by = "Indication",
            suffix = c("", "_True")) %>%
  mutate(Matching=pmap_lgl(list(Source, Source_True), identical)) %>%
  select(-Source_True)
```

3. Count occurrences & combine for the final data frame
```{r}
# Count occurrences per source and matching type
count_true <- multi_true_matching %>%
  count(Source, Matching, name="y_end") %>%
  mutate(DataOrigin="Ground Truth")

count_predictions <- multi_predictions_matching %>%
  count(Source, Matching, name="y_end") %>%
  # Invert y_end for mismatches
  mutate(y_end=if_else(Matching, y_end, -y_end)) %>%
  mutate(DataOrigin="Predicted Labels")


# Combine rows
count_combined <- count_true %>%
  bind_rows(count_predictions)
```

## Plot the data
```{r}
plt <- ggplot(count_combined, aes(x=Source)) +
  geom_col_pattern(aes(y=y_end, fill=DataOrigin,  pattern_density=Matching, group=DataOrigin), 
                   pattern_fill = "white",
                   pattern_colour = "white",
                   position=position_dodge(preserve = "single")) +
  scale_pattern_density_manual(values = c("TRUE" = 0.0, "FALSE"=0.2)) +
  scale_x_upset(n_intersections = 15) +
  
  xlab("Infection Source") +
  ylab("Intersection Size [Count]")

paste0(plot_path, sprintf("UpSet-Combination_MultiSource_%s.png", test_location)) %>%
  ggsave(plt,
         width = 25,
         height = 15,
         units = "cm")
```

