---
title: "Performance Metrics"
output: html_notebook
---
Regenerate the plots from python in R tidyverse to make them look prettier.


## Import data and libraries
Import libraries
```{r}
library(tidyverse)
require(tools)  # Base R library
theme_set(theme_light())  # or theme_light()

```
Define helper functions and variables
```{r}
categories = c('Abdominal', 'ENT', 'Neurological', 'No Specific Source', 'Not Informative', 'Orthopaedic', 'Other Specific', 'Prophylaxis', 'Respiratory', 'Skin & Soft Tissue', 'Urinary')

model = "Bio_ClinicalBERT"
```

### Read the data
```{r}
# Read the confusion matrices
confusion_matrix_banbury <- read_csv("/home/kevinyuan/EHR-Indication-Processing/03_Evaluation/tmp/Bio_ClinicalBERT_banbury_confusion_matrix_long.csv", col_types = cols(
  `True Label` = col_character(),
  `Predicted Label` = col_character(),
  Value = col_double()
  )) %>%
  mutate(
    `True Label` = fct_relevel(`True Label`, categories),
    `Predicted Label` = fct_relevel(`Predicted Label`, rev(categories))
  )

confusion_matrix_oxford <- read_csv("/home/kevinyuan/EHR-Indication-Processing/03_Evaluation/tmp/Bio_ClinicalBERT_oxford_confusion_matrix_long.csv", col_types = cols(
  `True Label` = col_character(),
  `Predicted Label` = col_character(),
  Value = col_double()
  )) %>%
  mutate(
    `True Label` = fct_relevel(`True Label`, categories),
    `Predicted Label` = fct_relevel(`Predicted Label`, rev(categories))
  )

# Read the f1 scores
f1_scores_banbury <- read_csv("/home/kevinyuan/EHR-Indication-Processing/03_Evaluation/tmp/Bio_ClinicalBERT_banbury_f1_scores.csv", col_types = cols(
      Source = col_character(),
      `F1 Score` = col_double()
    )
  ) %>% mutate(
    Source = fct_relevel(Source, categories)
  )

f1_scores_oxford <- read_csv("/home/kevinyuan/EHR-Indication-Processing/03_Evaluation/tmp/Bio_ClinicalBERT_oxford_f1_scores.csv", col_types = cols(
      Source = col_character(),
      `F1 Score` = col_double()
  )) %>%
  mutate(
    Source = fct_relevel(Source, categories)
  )
```


## Plot Graphs
Create single plots first (CM & F1 score bar plot) and then combine them into a single plot
1. Create Confusion Matrix plots
2. Create F1 score bar plots
3. Combine plots to multipanel figure (cowplot)

### Confusion Matrix
Function that creates the confusion matrix and returns a ggplot object
```{r}
plot_confusion_matrix <- function(confusion_matrix_long, model, location){
  plt <- confusion_matrix_long %>%
    ggplot(aes(x = `True Label`, y = `Predicted Label`)) +
      # --- Plot Values ---
      # Rectangles
      geom_tile(aes(fill = Value), colour = "grey92") +
      # Text
      geom_text(aes(label = sprintf("%.2f", Value)), size=2.5) +
    
      # --- Title, Axis and Scales ---
      labs(x = sprintf("Clinican Assigned Source\n (%s Data)", tools::toTitleCase(location)),
           y = "Predicted by Bio+Clinical BERT") +
  
      
      # --- Style ---
      # Theme
      # theme_minimal() +
    
      # Scale
      scale_fill_gradient(low = "#f5fafe", high = "steelblue") +
      # Guide style
      # guides(fill = guide_colourbar(barheight = 20)) +
      # Square tiles
      coord_equal() +
      # Rotate x-axis labels
      theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
  
  return(plt)
}

cm_oxford <- plot_confusion_matrix(confusion_matrix_oxford, model, "Oxford")
cm_banbury <- plot_confusion_matrix(confusion_matrix_banbury, model, "Banbury")
cm_oxford
```

### F1 Score Bar plots
Function that creates the F1 score bar plot and returns a ggplot object
```{r}
plot_f1_score <- function(f1_scores, model, location){
  plt <- f1_scores %>%
    ggplot(aes(x = Source, y = `F1 Score`)) +
      # --- Plot Values ---
      # Bars
      geom_bar(stat = "identity", fill = "steelblue") +
      # Text
      geom_text(aes(label = sprintf("%.2f", `F1 Score`)), vjust = -0.5, size=2.5) +
    
      # --- Title, Axis and Scales ---
      labs(x = NULL,  # Infection Source/Category",
           y = sprintf("F1 Score\n (%s Data)", tools::toTitleCase(location))) +
      ylim(NA, 1.1) +
  
      
      # --- Style ---
      # Theme
      # theme_minimal() +
      # theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
    
      # Rotate x-axis labels
      theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
  
  return(plt)
}

f1_oxford <- plot_f1_score(f1_scores_oxford, model, "Oxford")
f1_banbury <- plot_f1_score(f1_scores_banbury, model, "Banbury")
print(f1_oxford)
print(f1_banbury)
```

### Combine Plots
Try patchwork
```{r}
library(patchwork)
multiplot <- 
  (f1_oxford + labs(tag = "A")) + 
  (f1_banbury + labs(tag = "B")) +
  (cm_oxford + labs(tag = "C")) + 
  (cm_banbury + labs(tag = "D")) + 
  plot_layout(
      ncol = 2,
      nrow = 2,
      heights = c(1, 3)
    )

multiplot
ggsave("multiplot.png", multiplot, width = 30, height = 20, units = "cm")
ggsave("multiplot.pdf", multiplot, width = 30, height = 20, units = "cm")

```

