---
title: "Antibiotics Indication Matching"
output: html_notebook
---

Antibiotics dataset overview, with code snippets and some graphs to better understand this data.
```{r Loading libraries}
library(lubridate)
library(tidyverse)
library(stringi)
library(stringdist)
```

## Parse the data
Set the data path and maximum number of rows to read
```{r Setting up the Environment}
path_data <- '/home/shared/iord_extract_20220325'
path_cleaned <- '/home/kevinyuan/AMR-Project/00_Data/01_cleaned'
n_max <- Inf # Inf  # Set to 'Inf' for no limit
```

Read the data and parse into the correct format.
```{r Parsing the Data Antibiotics}
# Assemble path and read file
path_antibiotics <- paste(path_data, 'antibiotic_prescriptions.csv', sep = '/')
antibiotics_tbl <- read_csv(path_antibiotics, n_max = n_max, col_types = cols(
  Clusterid = col_double(),
  PrescriptionID = col_character(),
  PrescriptionDate = col_datetime(format = ""),
  PrescriptionStatus = col_factor(),
  PrescriptionType = col_factor(),
  AdmissionDate = col_date(format = ""),
  Drug = col_factor(),
  Formulation = col_character(),
  Dose = col_double(),
  DoseUnit = col_factor(),
  Frequency = col_factor(),
  Route = col_factor(),
  Indication = col_character(),
  ScheduledStartDateTime = col_datetime(format = ""),
  ScheduledStopDateTime = col_datetime(format = ""),
  DurationEnteredByPrescriber = col_character(),
  ReviewDateTime = col_datetime(format = ""),
  FirstAdministrationDateTime = col_datetime(format = ""),
  LastAdministrationDateTime = col_datetime(format = ""),
  NumberOfDosesAdministered = col_double(),
  SpecialInstructions = col_character(),
  AntibioticsSource = col_factor()
)) %>%
  # Rename the column `Clusterid` to `ClusterID`
  rename(ClusterID = Clusterid)

summary(antibiotics_tbl)
```
```{r Parsing the Data Episodes}
# Assemble path and read file
path_episodes <- paste(path_data, 'inpt_episode.csv', sep = '/')
episodes_tbl <- read_csv(path_episodes, n_max = n_max, col_types = cols(
  .default = col_datetime(),
  ClusterID = col_double(),
  SpellID = col_double(),
  EpisodeID = col_character(),
  LinkedSex = col_factor(),
  ConsultantMainSpecialtyCode = col_factor(),
  EthnicGroupCode = col_factor(),
  PostcodeStub = col_factor(),
  IMDScore = col_double(),
  ConsultantCodeAnon = col_factor(),
  AdmissionSourceCode = col_factor(),
  AdmissionMethodCode = col_factor(),
  DischargeDestinationCode = col_factor(),
  DischargeMethodCode = col_factor()
))

summary(episodes_tbl)
```

## Join Data
Join the `episodes_tbl` and `antibiotics_tbl` data.
Create two simplified data.frames with only needed columns ending in `_basic`.

We get the following data.frames used for further processing/analysis:
- Joined data: `episodes_antibiotics`

Use for quick analysis of indications:
- Extracted indication: `raw_indications`

```{r Join Episodes and Antibiotics data}
episodes_basic <- episodes_tbl %>%
  distinct(ClusterID, SpellID, AdmissionDate)

antibiotics_basic <- antibiotics_tbl %>%
  distinct(ClusterID, AdmissionDate, Indication, PrescriptionID)
  
episodes_antibiotics <- episodes_basic %>%
  mutate(AdmissionDate = as_date(AdmissionDate)) %>%
  inner_join(antibiotics_basic, by = c("ClusterID", "AdmissionDate")) %>%
  drop_na()

raw_indications <- episodes_antibiotics %>%
  select(Indication)
```

## Basic cleaning of the indication column
Cleaning steps:
1. Convert to lower case
2. Remove all non-sense indications

### Explore the dataset
**Analyse some non-character indications**
Show indication starts
```{r Show indication starting letters}
raw_indications %>%
  mutate(Indication_Start = str_sub(Indication, 1, 1), .keep = "used") %>%
  pull(Indication_Start) %>%
  table()
```

Show indications starting with non-letters or ?
```{r Show indications not starting with letters}
`%notin%` <- Negate(`%in%`)

raw_indications %>%
  filter(str_sub(Indication, 1 , 1) %notin% c(letters, LETTERS, "?"))
```

**Conclusion**
-> Probably want to filter (remove):
- Indications with only 1 character (except if it is `?`)
2. Indications not containing any letters or question mark (e. g. "..", "./", some numbers)

### Convert to all lowercase
```{r Convert indications to lowercase}
cleaning_tmp_lower <- episodes_antibiotics %>%
  mutate(IndicationRaw=Indication, IndicationCleaned=tolower(Indication), Indication=NULL)
```

### Remove unnecessary whitespaces (squish)
```{r Remove extra whitespaces}
cleaning_tmp_squished <- cleaning_tmp_lower %>%
  mutate(IndicationCleaned=str_squish(IndicationCleaned))
```

### Remove non-sense indications
Remove the following:
- Indications with only 1 character (except if it is `?`)
- Indications not containing any letters (e. g. "..", "./", some numbers)
```{r Remove non-sense indications}
cleaning_tmp_filtered <- cleaning_tmp_squished %>%
  # Minimal length
  filter(str_length(IndicationCleaned) > 1 | IndicationCleaned == "?") %>%
  # Must contain at least one letter
  filter(str_detect(IndicationCleaned, "[a-z\\?]"))
```

### [VIS] Show removed indications
```{r Show removed indications, purl=FALSE}
episodes_antibiotics %>%
  select(ClusterID, PrescriptionID, Indication) %>%
  anti_join(cleaning_tmp_filtered) %>%
  count(Indication, sort = TRUE)
```
### Finish the cleaning
```{r Rename temporary cleaning dataframe}
e_a_1_cleaned <- cleaning_tmp_filtered
```

## EDA for cleaned indications
```{r}
tmp_4000 <- e_a_1_cleaned %>%
  count(IndicationCleaned, sort=TRUE) %>%
  head(4000)
```

## Investigating original data source for the labelling
Clean the raw antibiotics table
```{r}
antibiotics_cleaned_indications <- antibiotics_tbl %>%
  mutate(Indication=tolower(Indication)) %>%
  mutate(Indication=str_squish(Indication)) %>%
  filter(str_length(Indication) > 1 | Indication == "?") %>%
  # Must contain at least one letter
  filter(str_detect(Indication, "[a-z\\?]"))
```


