---
title: "Upsample to original dataset"
output: html_notebook
---
Apply the classified indications back to the original dataset

## Load libraries and data
```{r}
library(tidyverse)
```

```{r}
data_base_path <- "00_Data/"

rxid_with_admission_path <- paste0(data_base_path, "RxID_within_admissions_all.csv")
predicted_labels_path <- paste0(data_base_path, "Indications_unique_classified.csv")

# full_indication <- read_csv(full_indication_path, show_col_types = FALSE) %>%
#   relocate(ClusterID, PrescriptionID, Indication)
full_abx_prescriptions <- read_csv("/home/shared/iord_extract_20220325/antibiotic_prescriptions.csv", col_types = cols(
  Clusterid = col_double(),
  PrescriptionID = col_character(),
  PrescriptionDate = col_datetime(format = ""),
  PrescriptionStatus = col_factor(),
  PrescriptionType = col_factor(),
  AdmissionDate = col_date(format = ""),
  Drug = col_factor(),
  Formulation = col_factor(),
  Dose = col_double(),
  DoseUnit = col_character(),
  Frequency = col_character(),
  Route = col_factor(),
  Indication = col_character(),
  ScheduledStartDateTime = col_datetime(format = ""),
  ScheduledStopDateTime = col_datetime(format = ""),
  DurationEnteredByPrescriber = col_character(),
  ReviewDateTime = col_datetime(format = ""),
  FirstAdministrationDateTime = col_datetime(format = ""),
  LastAdministrationDateTime = col_datetime(format = ""),
  NumberOfDosesAdministered = col_double(),
  SpecialInstructions = col_character(),
  AntibioticsSource = col_factor()
)) %>%
  relocate(ClusterID=Clusterid, PrescriptionID, Indication)

rxid_with_admission <- read_csv(rxid_with_admission_path, show_col_types = FALSE) %>%
  distinct(ClusterID, PrescriptionID)

```

## Filter for indications with followup data & export
Filter with Qingze's list & export the unique data to be classified
```{r}
# Filter
abx_prescriptions <- full_abx_prescriptions %>%
  # Cleanup
  drop_na(Indication) %>%
  mutate(Indication=tolower(Indication)) %>%
  distinct(ClusterID, PrescriptionID, Indication) %>%
  # Limit to Qingze's list of prescriptions
  inner_join(rxid_with_admission, by = c("ClusterID", "PrescriptionID"))

# Export
indications_unique_path <- paste0(data_base_path, "Indications_unique.csv")

abx_prescriptions %>%
  distinct(Indication) %>%
  write_csv(indications_unique_path)
```

## Predict
Run inference on the exported file.
Import the predictions file as "Indications_unique_classified.csv"

## Match back to the original dataset
Load the LUT
```{r}
indications_unique_classified_path <- paste0(data_base_path, "Indications_unique_classified.csv")

indication_label_lut <- read_csv(indications_unique_classified_path, show_col_types = FALSE)
```


```{r}
abx_prescriptions_classified <- abx_prescriptions %>%
  # Join back with the predicted labels. Classify the whole thing
  left_join(indication_label_lut, by="Indication")

rx_with_labels <- paste0(data_base_path, "RxID_with_labeles.csv")
abx_prescriptions_classified %>%
  write_csv(rx_with_labels)
```

